---
title: "ggplot2 course optional homework"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tidy Tuesday

Try your hand at visualizing this week's Tidy Tuesday [data](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020). (Look for the folder named for today's date.) You should aim to make at least 3 visualizations: 

1. A one-variable viz
2. A two-variable viz
3. A three or more variable viz

Email me your favorite and I will put them in the slides at the beginning of day 2. (tyner.samantha@bls.gov)

## Load packages & Read in the data 

```{r getdata}
library(ggplot2)
library(readr)
library(dplyr)
# or 
# library(tidyverse)

# put the name of the file where {filename} is 
gdpr <- read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-21/gdpr_violations.tsv')
```

## Use code chunks to make plots 

```{r plot1}
# chris nolte
ggplot(dat, aes(x=name)) +
  geom_histogram(stat='count') +
  labs(x='Country', y='Number of Violations') +
  theme(axis.text.x=element_text(angle=90, hjust=1))

dat %>% 
  group_by(name) %>% 
  count() %>% 
  ggplot(aes(x=reorder(name,-n), y = n)) +
  geom_col() +
  labs(x='Country', y='Number of Violations') +
  theme(axis.text.x=element_text(angle=90, hjust=1))
```


```{r plot2}
# your code here (two variable viz)
```

```{r plot3}
# your code here (three+ variable viz) 
```
